Ecuador plant species TRY data

### 2023-01-12 code/L0/L0_Ecuador_plants_TRY.Rmd
Add output information to header

---
title: "Ecuador plant species TRY data"
author: "Hazel J. Anderson"
collaborators: "None"
data input: "None"
data output: "TBD"
project: "Frugivoria"
date: "2022-10-27"
output: html_document
---

@@

### using summarytools package
```{r}
ecuador_TRY_plant_traits_summary <- dfSummary(data, 
            na.col       = FALSE,
            style        = "multiline",
            plain.ascii  = TRUE,
            graph.magnif = .8)
print(ecuador_TRY_plant_traits_summary, method = "render")
view(ecuador_TRY_plant_traits_summary, file = file.path(output_path,"ecuador_TRY_plant_traits_summary.html"))
# gives the following error: Error in withCallingHandlers(expr, warning = function(w) if (inherits(w, : 
#   invalid multibyte string at '<b0>45''
```

>>>>

---
title: "Ecuador plant species TRY data"
author: "Hazel J. Anderson"
collaborators: "None"
data input: "None"
data output: "Ecuador_TRY_plant_traits.csv"
project: "Frugivoria"
date: "2022-10-27"
output: html_document
---

@@

### using summarytools package
```{r}
ecuador_TRY_plant_traits_summary <- dfSummary(data, 
            na.col       = FALSE,
            style        = "multiline",
            plain.ascii  = TRUE,
            graph.magnif = .8)
print(ecuador_TRY_plant_traits_summary, method = "render")
view(ecuador_TRY_plant_traits_summary, file = file.path(output_path,"Ecuador_TRY_summary.html"))
# gives the following error: Error in withCallingHandlers(expr, warning = function(w) if (inherits(w, : 
#   invalid multibyte string at '<b0>45''
```
